STA610 Case Study 1 Team 4 Report

### 2021-03-22 final_report.Rmd
Moved some EDA to appendix

We find that there are many cities with a sample size of one, which makes `city` perhaps not the most natural choice for a grouping variable. Example visualizations shown here are for all cities in the states of Florida and California.

```{r, fig.align='center'}
fl_lppmbycity <- ggplot(df[df$state=="Florida",], aes(x=log_ppm, y=reorder(city, city, length))) +
geom_boxplot() +
labs(title="log PPM by city (FL)", x="Log PPM",y="city")
ca_lppmbycity <- ggplot(df[df$state=="California",], aes(x=reorder(city, city, length), y=log_ppm)) +
geom_boxplot() +
labs(title="log PPM by city (CA)", x="Log PPM",y="city")
grid.arrange(fl_lppmbycity, ca_lppmbycity, ncol= 2)
```

We decided to focus on `state` as our primary candidate for a grouping variable moving forward.

@@

## More EDA: slope and intercept distributions for predictors by state

To get a better sense of how state-level groups and slopes are distributed, we created the following intercepts for our coninuous variables:

```{r fig.width=3}
group_int_list <- NULL 
group_slope_list <- NULL
for(statej in unique(df$state)) {
    m <- lm(data = df[df$state==statej, ], log_ppm ~ dose_per_mg)
    group_int_list <- c(group_int_list, coef(m)[1])
    group_slope_list <- c(group_slope_list, coef(m)[2])
}
hist(group_int_list)
hist(group_slope_list)
```

```{r fig.width=3}
group_int_list <- NULL 
group_slope_list <- NULL
for(statej in unique(df$state)) {
    m <- lm(data = df[df$state==statej, ], log_ppm ~ date_num)
    group_int_list <- c(group_int_list, coef(m)[1])
    group_slope_list <- c(group_slope_list, coef(m)[2])
}

hist(group_int_list)
hist(group_slope_list)
```

@@

## Appendix
```{r, ref.label=knitr::all_labels(), echo=TRUE, eval=FALSE}
```

>>>>

We find that there are many cities with a sample size of one, which makes `city` perhaps not the most natural choice for a grouping variable (please see appendix). We decided to focus on `state` as our primary candidate for a grouping variable moving forward.

@@

@@

## Appendix
```{r, ref.label=knitr::all_labels(), echo=TRUE, eval=FALSE}
# Example visualization shown here are for all cities in the state of Florida.

ggplot(df[df$state=="Florida",], aes(x=log_ppm, y=reorder(city, city, length))) +
geom_boxplot() +
labs(title="log PPM by city (FL)", x="Log PPM",y="city")

# More EDA: slope and intercept distributions for predictors by state

# To get a better sense of how state-level groups and slopes are distributed, we created the following intercepts for our coninuous variables:

group_int_list <- NULL 
group_slope_list <- NULL
for(statej in unique(df$state)) {
    m <- lm(data = df[df$state==statej, ], log_ppm ~ dose_per_mg)
    group_int_list <- c(group_int_list, coef(m)[1])
    group_slope_list <- c(group_slope_list, coef(m)[2])
}
hist(group_int_list)
hist(group_slope_list)

group_int_list <- NULL 
group_slope_list <- NULL
for(statej in unique(df$state)) {
    m <- lm(data = df[df$state==statej, ], log_ppm ~ date_num)
    group_int_list <- c(group_int_list, coef(m)[1])
    group_slope_list <- c(group_slope_list, coef(m)[2])
}

hist(group_int_list)
hist(group_slope_list)

```
